Missing the Point: Non-Convergence in Iterative Imputation Algorithms

### 2020-05-06 3.Thesis/Writeup/2.Manuscript.Rmd
Re-structure repo to make clear how Figures are created.

# packages
library(dplyr)
library(ggplot2)
library(patchwork)

# results and functions
load("../Results/complete.Rdata") 
results <- results %>% filter(t<50)
source("../2.CreateFigures.R")

# default graphing behavior
theme_update(
 plot.title = element_text(hjust = 0.5),
 plot.subtitle = element_text(hjust = 0.5),
 panel.border = element_blank(),
 panel.grid.major = element_blank(),
 panel.grid.minor = element_blank(),
 panel.background = element_blank(),
 axis.line = element_line(colour = "black"),
 legend.key = element_blank(),
 legend.position = "bottom",
 legend.margin = margin(0,0,0,0),
 # adjust text size
 text = element_text(size = 8),
 title = element_text(size = 8),
 legend.title = element_text(size = 7)

 # axis.title = element_text(size = 8),
 # axis.text = element_text(size = 7),
 # legend.text = element_text(size = 7)
)
```

@@

```{r diagram, out.width="\\linewidth", include=TRUE, fig.cap="Scheme of the main steps in multiple imputation (where $M=3$)---from an incomplete dataset, to $M$ multiply imputed datasets, to $M$ estimated quantities of scientific interest $\\hat{Q}$s, to a single pooled estimate $\\bar{Q}$."}
knitr::include_graphics("./images/diagram.pdf") #adapted from [@buur18] par. 1.4.1.
```

@@

```{r non-conv, out.width='.49\\linewidth', fig.width=3.5, fig.height=3,fig.show='hold',fig.cap="Typical convergence versus pathological non-convergence. Please note that this is the same data with a different imputation model, leading to different imputations (e.g., see the units on the y-axis)."}
load("./images/nonc_plot.Rdata")
load("./images/conv_plot.Rdata")
par(mar = c(2, 2, 0.1, 0.1))
plot(conv)
plot(nonc)
```

@@

```{r diagnostics, fig.cap="Convergence diagnostics applied on the imputation algorithms of Figure 2. $\\theta$ = chain mean in $y_{imp, m}$."}
load("./images/diagnostics_plot.Rdata") #bquote(theta ~ "= chain mean in "~ y[imp][",m"])
diagnostics_plot 
```

@@

Convergence of the MICE algorithm is investigated through model-based simulation in `R` [version `r paste(version$major,version$minor, sep = ".")`; @R]. The simulation set-up is summarized in the pseudo-code below. The complete `R` script of the simulation study is available from [github.com/gerkovink/shinyMice](https://github.com/gerkovink/shinyMice/tree/master/3.Thesis/1.SimulationStudy).

>>>>

# packages
library(mice)
library(dplyr)
library(ggplot2)
library(patchwork)

# load example non-convergence and figures
load("../Results/example_nonconv.Rdata")
load("../Results/example_conv.Rdata")
load("../Results/example_diagnostics.Rdata")
source("../3.PlotExampleNon-convergence.R")

# load results and figures
load("../Results/complete.Rdata") 
results <- results %>% filter(t<51)
source("../4.PlotResults.R")

# default graphing behavior
theme_update(
 plot.title = element_text(hjust = 0.5),
 plot.subtitle = element_text(hjust = 0.5),
 panel.border = element_blank(),
 panel.grid.major = element_blank(),
 panel.grid.minor = element_blank(),
 panel.background = element_blank(),
 axis.line = element_line(colour = "black"),
 legend.key = element_blank(),
 legend.position = "bottom",
 legend.margin = margin(0,0,0,0),
 # adjust text size
 text = element_text(size = 8),
 title = element_text(size = 8),
 legend.title = element_text(size = 7)
)
```

@@

```{r diagram, out.width="\\linewidth", include=TRUE, fig.cap="Scheme of the main steps in multiple imputation (where $M=3$)---from an incomplete dataset, to $M$ multiply imputed datasets, to $M$ estimated quantities of scientific interest $\\hat{Q}$s, to a single pooled estimate $\\bar{Q}$."}
knitr::include_graphics("../Figures/diagram.pdf") #adapted from [@buur18] par. 1.4.1.
```

@@

```{r non-conv, out.width='.49\\linewidth', fig.width=3.5, fig.height=3,fig.show='hold',fig.cap="Typical convergence versus pathological non-convergence. Please note that this is the same data with a different imputation model, leading to different imputations (e.g., see the units on the y-axis)."}
par(mar = c(2, 2, 0.1, 0.1))
con_plot
non_plot
```

@@

```{r diagnostics, fig.cap="Convergence diagnostics applied on the imputation algorithms of Figure 2. $\\theta$ = chain mean in $y_{imp, m}$."}
# load("./images/diagnostics_plot.Rdata") #bquote(theta ~ "= chain mean in "~ y[imp][",m"])
(theta + plot_layout(guides = "collect", ncol = 2)) + (ac_both + plot_layout(guides = "keep")) + old_rhat + new_rhat +  plot_annotation(tag_levels = "A", tag_suffix = ".") # add 'ncol=1' for plots under each other
```

@@

Convergence of the MICE algorithm is investigated through model-based simulation in `R` [version 3.6.3; @R]. The simulation set-up is summarized in the pseudo-code below. The complete `R` script of the simulation study is available from [github.com/gerkovink/shinyMice](https://github.com/gerkovink/shinyMice/tree/master/3.Thesis/1.SimulationStudy).

### 2020-05-06 3.Thesis/Writeup/2.Manuscript.tex
Re-structure repo to make clear how Figures are created.

{\centering \includegraphics[width=\linewidth]{./images/diagram}

@@

{\centering \includegraphics[width=.49\linewidth]{manuscript_files/figure-latex/non-conv-1} \includegraphics[width=.49\linewidth]{manuscript_files/figure-latex/non-conv-2}

@@

{\centering \includegraphics{manuscript_files/figure-latex/diagnostics-1}

@@

{\centering \includegraphics{manuscript_files/figure-latex/Qs-1}

@@

{\centering \includegraphics{manuscript_files/figure-latex/rhats-acs-1}

>>>>

{\centering \includegraphics[width=\linewidth]{../Figures/diagram}

@@

{\centering \includegraphics[width=.49\linewidth]{2.Manuscript_files/figure-latex/non-conv-1} \includegraphics[width=.49\linewidth]{2.Manuscript_files/figure-latex/non-conv-2}

@@

{\centering \includegraphics{2.Manuscript_files/figure-latex/diagnostics-1}

@@

{\centering \includegraphics{2.Manuscript_files/figure-latex/Qs-1}

@@

{\centering \includegraphics{2.Manuscript_files/figure-latex/rhats-acs-1}
